{{< var titll >}}

### 2024-08-01 abc.qmd
abc

---
title: ""
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table','readr','ggplotly']             # Pre-install dependencies
  cell-options:
    autorun: true
filters:
  - panelize
  - pyodide
  - webr
---

## Web-R

:::{.to-webr}
```{r}
1 + 1
```
:::

## Pyodide

:::{.to-pyodide}
```{python}
x = [1, 2]
print(x)
```
:::

>>>>

---
title: "{{< var titll >}}"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs:
    drop:
      engine: webr
      webr:
        packages:
          - ggplot2
          - dplyr
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

# Abc

2+2
